\thetitle

### 2021-05-25 writing/discussion.tex
Small fixes from meeting last week
new subsection on threats

The validity of these conclusions is threatened in several ways: (i) the
representativeness of benchmarks; (ii) the relation between mutations and real
programming mistakes; (iii) the definition of interesting debugging scenarios;
and (iv) the sampling strategy. While these threats have been mitigated by the
experimental setup, the remainder of this section discusses three additional
ones.

%% -----------------------------------------------------------------------------
\subsection{Threat: Is the Rational Programmer Realistic?}

>>>>

%% -----------------------------------------------------------------------------
\subsection{What Are the Threats to Validity?}

The validity of these conclusions is threatened in two fundamentally distinct
ways. The first sets of threats have been mentioned before: (i) the
representativeness of benchmarks; (ii) the relation between mutations and real
programming mistakes; (iii) the definition of interesting debugging scenarios;
and (iv) the sampling strategy.  While the experimental setup attempts to
mitigate against these threats, the reader must definitely take into account
these limitations of the experiment and must understand that the collected data
not support any further generalization.

The second set of threats connects the experiment with reality or, more
precisely, assess how close the connection is. To start with, it questions the
realism of the rational programmer itself (sec.~\ref{sub:rational}), followed by
the definition of ``interesting scenarios''
(sec.~\ref{sec:threat:erasure-bias}).  The remaining questions address the
accuracy and the cost of Transient blame, respectively (see
secs.~\ref{sec:threat:transient} and~\ref{sec:threat:transient2}).

%% -----------------------------------------------------------------------------
\subsection{Threat: Is the Rational Programmer Realistic?} \label{sub:rational}
